Supplemental Materials

### 2021-07-20 supplement/supplement-main.Rmd
updated model figs

export_graph(z2, "../local/boot-graph.pdf")
```

@@

cowplot::save_plot("../local/boot-graph-legend.svg", boot_graph_legend)
# cowplot::ggdraw(boot_graph_legend)
```

@@

## assemble bootstrapping graph and legend into pdf and display here
knitr::include_graphics("../local/boot-graph.pdf") 
```

@@

# export graph image
export_graph(z, "../local/main-graph.pdf")
# render_graph(z)
```

@@

cowplot::save_plot("../local/graph-legend.svg", main_graph_legend)
# cowplot::ggdraw(main_graph_legend)

@@

## assemble main model graph and legend into pdf and display here (main-graph-combined.pdf)
## currently just the output graph w/ no legend (main-graph.pdf)
knitr::include_graphics("../local/main-graph.pdf") 
```

>>>>

export_graph(z2, "../outputs/boot-graph.pdf")
```

@@

cowplot::save_plot("../outputs/boot-graph-legend.svg", boot_graph_legend)
# cowplot::ggdraw(boot_graph_legend)
```

@@

## assemble bootstrapping graph and legend into pdf and display here
knitr::include_graphics("../outputs/boot-combined.pdf") 
```

@@

# export graph image
export_graph(z, "../outputs/main-graph.pdf")
# render_graph(z)
```

@@

cowplot::save_plot("../outputs/graph-legend.svg", main_graph_legend)
# cowplot::ggdraw(main_graph_legend)

@@

## assemble main model graph and legend into pdf and display here (main-graph-combined.pdf)
## currently just the output graph w/ no legend (main-graph.pdf)
knitr::include_graphics("../outputs/main-combined.pdf") 
```
